\textit{Red Oak}: Proactive Policy Generation

### 2015-05-10 draft.tex
..

\title{Red Oak: Proactive Policy Generation}
 \authorinfo{Ryan Beckett}{Princeton University}{rbeckett@princeton.edu}
 \authorinfo{Olivier Savary B\'{e}langer}{Princeton University}{olivierb@princeton.edu}

@@

val in_rel: packet -> field list -> relation-> bool
\end{lstlisting}

@@

We implemented in Red Oak, under \lstinline|o1|, a local transformation adding an \lstinline|in_rel| node before \lstinline|add| or \lstinline|remove| nodes. In the case of \lstinline|add|, the \lstinline|add| node is omited in the true branch of \lstinline|in_rel|, such that packets whose fields are already in the relation will not be seen by the controller due to this \lstinline|add| node. Similarly, we omit the \lstinline|remove| node in the false branch of \lstinline|in_rel|. In the firewall example (see Fig.~\ref{fig:firewallcode}), this would result the following decision tree:

\begin{figure}[ht]
  TODO
\caption{Optimized Decision Tree for Stateful Firewall}     
\label{fig:decisiontreeopt}  
  \end{figure}

>>>>

\title{\textit{Red Oak}: Proactive Policy Generation}
 \authorinfo{Ryan Beckett}{Princeton University}{rbeckett@princeton.edu}
 \authorinfo{Olivier Savary B\'{e}langer}{Princeton University}{olivierb@princeton.edu}

@@

val in_rel: packet -> field list -> relation
    -> bool
\end{lstlisting}

@@

We implemented in \textit{Red Oak} a local transformation adding an \lstinline|in_rel| node before \lstinline|add| or \lstinline|remove| nodes. In the case of \lstinline|add|, the \lstinline|add| node is omited in the true branch of \lstinline|in_rel|, such that packets whose fields are already in the relation will not be seen by the controller due to this \lstinline|add| node. Similarly, we omit the \lstinline|remove| node in the false branch of \lstinline|in_rel|. In the firewall example (see Fig.~\ref{fig:firewallcode}), this would result the following decision tree:

\begin{figure}[ht]
  \includegraphics[scale=.33]{img/optdtree.png}
\caption{Optimized Decision Tree for Stateful Firewall}     
\label{fig:decisiontreeopt}  
  \end{figure}
